---
title       : Simple Date Calculator
subtitle    : for devdataprod-010 course project
author      : 
job         : 
framework   : dzslides        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Agenda

1.  Purpose
2.  How to use the application
3.  Sample R code

--- .class #id 

## Purpose

1.  This is a very simple Shiny application that calculates the date when a person's age will be double another person's age 

--- .class #id 

## How to use

1.  Simply input the birthdates of two people you know


--- .class #id 

## Sample R code

1. Let's consider two people with the following birthdates:
```{r}
older <- as.Date("1960-06-01")
younger <- as.Date("1980-01-01")
```
2. Then the date we are looking for is computed as follows:
```{r}
older + 2 * (younger - older)
```


--- .class #id 

## Thank you!




